\propertitle

### 2020-03-17 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T12:05:53+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

Second, the \enquote{complexity} of a model cannot be judged from the
dimensionality of its family. Models $M_{1}$ and $M_{2}$ can have the same
family, but $M_{1}$ can have a family distribution concentrated on a very
small region, with respect to that of $M_{2}$. Model $M_{1}$ is thus
effectively using a smaller parameter range than $M_{2}$. Correspondingly
the \enquote{typical set} of data to which $M_{1}$ assigns appreciable
probability is smaller than the typical set of $M_{2}$: model $M_{1}$ is
less \enquote{powerful}. The effective dimensionality, complexity, or power
of a model is thus best defined by the volume of \emph{data space} that is
typical under that model. Most important, it may then happen that a model
is more powerful than another even if it is based on a lower-dimensional
family.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T12:14:41+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

Second, the \enquote{complexity} of a model cannot be judged from the
dimensionality of its family. Models $M_{1}$ and $M_{2}$ can have the same
family, but $M_{1}$ can have a family distribution concentrated on a very
small region, with respect to that of $M_{2}$. Model $M_{1}$ is thus
effectively using a smaller parameter range than $M_{2}$. Correspondingly
the \enquote{typical set} of data to which $M_{1}$ assigns appreciable
probability is smaller than the typical set of $M_{2}$: model $M_{1}$ is
less \enquote{powerful}. The effective dimensionality, complexity, or power
of a model is thus best defined by the volume of \emph{data space} that is
typical under that model \citep[an \enquote{effective dimensionality} of
the family can be calculated from this volume:][\sect~4]{mackay1992}. Most
important, it may then happen that a model is more powerful than another
even if it is based on a lower-dimensional family
\citep[\sect~6]{mackay1992}[esp.\ Fig.~4]{mackay1992b}.
